Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-14 papers/B1555_EdgeOn/B1555_letter.tex
Additional text for Section 2

While future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies. 
In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex lens galaxy mass distribution than initially considered. To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP). The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12,V12} . In particular, to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging. \simona{The paper is organized as follows: the latest SHARP data is introduced in section 2; in section 3 we present the lens model while the results of this analysis and their implication are discussed in section 4.}
%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}. 
%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems. 
%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. 
%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A ??x?? cutout of the final reduced image
is shown in Fig.~??b and again in Fig.~??c with contours from the
MERLIN radio observations of \citet{Marlow} overlaid.

\section{Lens Modelling}
To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this new information from A/O image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

>>>>

While future large-scale surveys, such as the LSST, \simona{are
  expected to deliver new large samples of gravitationally lensed
  quasar, in the near future the discovery of new systems using}
narrow-line quasar emission \citep{N14} \simona{will provide new
  invaluable statistical perspective on current constraints based on
  flux ratio anomalies.  In this paper, we explore the alternative
  idea that flux ratio anomalies are not related to the presence of
  substructure but originate in a more complex lens galaxy mass
  distribution than initially considered. To this end we use new
  infra-red data from the Strong lensing at High Angular Resolution
  Program(SHARP). The main goal of the SHARP} project \simona{is to
  re-observe} known quadruple and Einstein ring lens systems at a much
higher angular resolution by making use of the Keck adaptive optics
(AO) telescope and large interferometric arrays \citep{SHARP12,V12}
. In particular, to better understand the cause of flux ratio
anomalies in strong lens systems \simona{we focus on the lens
  modelling of the lens system B1555+375 (included in both the
  observational and theoretical analysis of \citet{Dalal2002} and
  \citet{Xu14}, respectively) by making use of} the new information
obtained from the latest SHARP infrared imaging. \simona{The paper is
  organized as follows: the latest SHARP data is introduced in section
  2; in section 3 we present the lens model while the results of this
  analysis and their implication are discussed in section 4.}

%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}. 
%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems. 
%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. 
%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A ??x?? cutout of the final reduced image
is shown in Fig.~??b and again in Fig.~??c with contours from the
MERLIN radio observations of \citet{Marlow} overlaid.  There are several
notable features in the Keck AO data.  These
include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible emission
from what appears to be an edge-on lensing galaxy.

@@

The B1555+375 system was also observed by the Hubble Space Telescope
(HST) in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the $F555W$ and $F814W$ bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival HST
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
MATT], producing final drizzled images with pixel scales of
50~mas.  The reduced images are shown in Figure~??.  The lens system
is not detected at high significance in the optical bands, but is
clearly seen in the NICMOS $F160W$ image.  The edge-on lensing galaxy 
stands out in the NICMOS image.

%===========================================================================

\section{Lens Modelling}

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this new information from A/O image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)
